\large{\bf Abnormal quantitative genetics? }

### 2023-07-03 writeup.tex
step things

>>>>

\begin{figure}
    \begin{center}
        \includegraphics{sims/neutral_trait_traces}
    \end{center}
    \caption{
        Median trait values over time \textbf{(A and C)}
        and distributions of final trait values \textbf{(B and D)}
        in neutral simulations
        with Normal \textbf{(A and B)} and Cauchy \textbf{(C and D)}
        effect size distributions.
        Simulations were begun with no genetic variation,
        had populations of size $N=1000$,
        a genome of length $L=10^8$ and mutation rate of $\mu=10^{-9}$;
        the effect size distributions were
        Normal with mean 0 and standard deviation $1/\sqrt{4NL\mu}$
        and Cauchy with center 0 and scale $1/(4NL\mu)$, respectively.
        \label{fig:trait_distrns}
    }
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{sims/selected_trait_traces}
    \end{center}
    \caption{
        Median trait values over time \textbf{(A and C)}
        and distributions of final trait values \textbf{(B and D)}
        in neutral simulations
        with Normal \textbf{(A and B)} and Cauchy \textbf{(C and D)}
        effect size distributions.
        Simulations were begun with no genetic variation,
        had populations of size $N=1000$,
        a genome of length $L=10^8$ and mutation rate of $\mu=10^{-9}$;
        the effect size distributions were
        Normal with mean 0 and standard deviation $1/\sqrt{4NL\mu}$
        and Cauchy with center 0 and scale $1/(4NL\mu)$, respectively.
        \label{fig:trait_distrns}
    }
\end{figure}
